---
output:
  html_document:
    keep_md: true
    pandoc_args: [
      "+RTS", "-K10000000",
      "-RTS"
    ]
    toc: true
    toc_depth: 4    
---

*This documentation is embedded from Depsy's GitHub Readme, and is still in progress. Feel free to submit a pull request with updates and changes*

```{r setup, echo=FALSE}
library(knitr)
opts_knit$set(progress=TRUE, tidy=TRUE)
```

```{r load_libraries, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(magrittr)
library(ggplot2)
library(dplyr)
library(broom)
library(RJDBC)
```

```{r get_data, echo=FALSE, results='hide', cache=TRUE}
pgsql <- JDBC("org.postgresql.Driver", "~/Dropbox/ti/depsy r/postgresql-9.4-1203.jdbc4.jar", "`")
my_db <- dbConnect(pgsql, 
                   "jdbc:postgresql://ec2-54-227-249-158.compute-1.amazonaws.com:6222/dh6mnd776vk3a?ssl=true&sslfactory=org.postgresql.ssl.NonValidatingFactory", 
                   password="p1ohgjb5peg9ro29fmogsp85k8g", 
                   user="ufvsf5ekesp7ls")

raw_package_data = dbGetQuery(my_db, "
    select 
        id, 
        host,
        impact, 
        impact_percentile,
        num_downloads,
        num_downloads_percentile,
        num_citations,
        num_citations_percentile,
        pagerank,
        pagerank_score,
        pagerank_percentile,
        indegree,
        neighborhood_size
    from package 
    where is_academic = true")

## get data ready for dplyr
dp = tbl_df(raw_package_data)

## see what we've got
glimpse(dp)

```


##Depsy is a better way to learn the impact of research software.##
It's being built at [Impactstory](https://impactstory.org/about) by Jason Priem and Heather Piwowar, and is funded by an [EAGER grant](http://blog.impactstory.org/impactstory-awarded-300k-nsf-grant/) from the National Science Foundation.

## What does Depsy include?

Depsy finds the impact of research software **packages** written in Python and R, and also impact of the **people** who write it.

[PyPI](http://pypi.python.org) for Python, and [CRAN](https://cran.r-project.org/web/packages/) for R.

R is a language for doing statistics.  As such, almost all of its packages are written by academics, for academics, to do reasearch--so we consider all R software on Depsy to be research software. We cover the *`r dp %>% filter(host=='cran') %>% nrow()`* R software packages available on [CRAN](https://cran.r-project.org/web/packages/), the main library repository for R.


Python is a more general purpose programming language.  We try to establish whether a given Python package is research software by searching its metadata (package name, description, tags) for researchy-words (see [code on GitHub](https://github.com/Impactstory/depsy/blob/870c85ee4598643f496bca76e5a7dff994e53837/models/academic.py)). We cover all *57,243* active Python packages on [PyPI](http://pypi.python.org), Python's main package repository; of those, we count *`r dp %>% filter(host=='pypi') %>% nrow()`* as research software.

## Package impact

We currently calculate impact along three dimensions (and a fourth, coming later, that will capture social signals like GitHub watchers and Stack Overflow discussions). The overall impact score of a package is calculated as the average of these three: **downloads**, **software reuse**, and **literature mentions**. 

More information coming soon!  In the mean time, see our [full documentation page](https://github.com/Impactstory/depsy-research/blob/master/introducing_depsy.md) for details.


